Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-04-08 Cost_manuscript.Rmd
methods and results draft (sans OC modeling on cost3)

## plot
earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) +
         scale_color_manual(values = colsBtw) +
         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = F) +
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsBtw) +
         theme(panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(),
           panel.background = element_blank(),
           axis.line = element_line(colour = "black"),
           text = element_text(size = 12))

@@

```{r General prop & earnings plots (Fig. 3), fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least."}
# plots generated in 16.2.1. and 16.1.3.
 prop1 | earnings1 | earnFitplot
```

@@

# plot coefficients and pvalues in a matrix
# invert colors
col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))

corrplot(mixSummary_btw$Betas, 
         is.corr = F, 
         p.mat = mixSummary_btw$Pvals, 
         type = "lower",
         outline = T,
         #insig = "p-value",
         sig.level = 0.05, 
         na.label = "square", 
         na.label.col = "grey",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.8,
         col = col2(200))

@@

  In order to test these qualitative observations, we computed the probability of accepting a trial with a mixed-effects logistic regression (see Methods for details). As predicted, and confirming previous results, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`). In order to show the comparisons among all conditions, Figure 4B portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons). The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical and wait groups, but not the easy group.

@@

``` {r BTW: 16.3.2. Plot Pre/Post, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# scatter plot of pre/post acceptances
# first calculate the mean acceptances per cost/half to draw horizontal and vertical lines on the plot
df_mean <- dataBtw %>%
            group_by(SubjID, Cost, Block, Half) %>%
            summarise(propAccept = mean(Choice)) %>%
            group_by(SubjID, Cost, Half) %>%
            summarise(propAccept = mean(propAccept)) %>%
            spread(Half, propAccept) %>%
            group_by(Cost) %>%
            summarise(propAccept_1 = mean(Half_1),
                      propAccept_2 = mean(Half_2))

@@

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost_btw$propBlocks <- dataBtw %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice)) %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs_btw)) %>%
                         ggplot(aes(Block, propAccept, color = Cost)) +
                           geom_vline(xintercept = 3.5, linetype = "dashed") +
                           geom_point(size = 2) +
                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line() +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = colsBtw) +
                           scale_fill_manual(values = colsBtw) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.25),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 14))

@@

``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
prepostPlot <-dataBtw %>%
  group_by(SubjID) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half")) %>%
  group_by(SubjID, Half, Handling, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Handling, Offer) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  ggplot(aes(Offer, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = T) +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = colsBtw) +
    scale_fill_manual(values = colsBtw) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted") +
    facet_wrap(vars(Handling, Half), ncol = 2) +
    theme(legend.position = "bottom",
          strip.text.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

@@

``` {r WTH: 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width=4,fig.height=4}
# Notes: I also performed this comparing halves and block types x half, and it doesn't look like participants were accepting less to make more.
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataWth %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

# plot
(earnFitplot <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = colsWth) + 
         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsWth) +
         ylim(12, 16) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16)))

@@

  Analyses from the previous experiment were repurposed to examine cost differences within individuals. We begun by testing the prediction that rewards would positively influence choices. A Wilcoxon signed rank test showed that individual logistic coefficients for reward amount were significantly greater than 0 (mean $\beta$ = `r round(mean(baseCoeffs$Offer), digits = 2)`, SD = `r round(sd(baseCoeffs$Offer), digits = 2)`; V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* `r report_p(wilcox.test(baseCoeffs$Offer)$p.value)`), once again confirming that participants were properly influenced by reward amounts. Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history, thus discarding systematic sequential effects. In terms of earnings, a linear model predicting earnings once again showed that participants who accepted too few or too many trials earned the least, in line with the experimental design (Figure X; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`). When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05). Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait_C = `r filter(earnings_within, Cost == "Wait_C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait_P = `r filter(earnings_within, Cost == "Wait_P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_P")$sdEarn`). These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**big caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward. So neither approach really gets at this too well.**).

@@

# plot proportion accepted per trial/offer combo
(n2 <- dataWth %>%
        filter(Choice < 2) %>%
        group_by(Cost, Offer) %>%
        summarise(propAccept = mean(Choice),
                  SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
        ungroup() %>%
        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataWth$Cost))),
               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
               Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, propAccept, color = Cost)) +
          geom_point(size = 3, show.legend = T) +
          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
          geom_line(lwd = 1, show.legend = T) +
          scale_color_manual(values = colsWth) +
          scale_fill_manual(values = colsWth) +
          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
          labs(y = "Proportion Accepted") +
          theme(legend.position = c(0.8, 0.25),
                legend.key = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"),
                text = element_text(size = 22)))

@@

``` {r WTH: 16.2.1. mixed effects matrix, echo = FALSE, fig.align = "center", fig.width = 5,  fig.height = 4}
# get summary of coeffs
rearrange <- c("Cognitive", "Wait_C", "Wait_P", "Physical")
mixSummary <- betaMatrix(mixLogis_main, rearrange = rearrange)
diag(mixSummary$Pvals) <- NA

# remove uninteresting comparisons
mixSummary$Betas[rbind(c(3, 1), c(4,2))] <- NA
mixSummary$Pvals[rbind(c(3, 1), c(4,2))] <- NA

# invert colors
col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))

corrplot(mixSummary$Betas, 
         is.corr = F, 
         p.mat = mixSummary$Pvals, 
         type = "lower",
         outline = T,
         #insig = "p-value",
         sig.level = 0.05, 
         na.label = "square", 
         na.label.col = "grey",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.8,
         col = col2(200))

@@

``` {r WTH: 16.2.2. ME model comparison, echo = FALSE, fig.align="center", fig.width=6, fig.height=4}
# fit ME logistic at increasing model complexities
mixLogis_compare <- list()
mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$AllMain <- mixLogis_main$Cognitive
mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (1 | SubjID), family = "binomial", data = mixData)

@@

# plot 
(mixLogis_compare$plot <- abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
  ggplot(aes(Model, Value, fill = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
    theme_classic())

@@

  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones. As can be seen on Figure X, even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure X), differences among cost conditions were less evident. Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand. We tested this observation through a mixed effects logistic regression, with main fixed effects for offer amount and cost, and random subject-wise intercepts (the reference cost category was rotated in order to perform all possible pairwise comparisons). The model confirmed that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`). As in the previous section, pairwise comparison results are shown on the matrix in Figure X. This plot omits comparisons between effort and wait trials from different blocks, as these are not considered in our original predictions **(rephrase, with the understanding that Wait_C > Physical)**. The only significant difference was the higher likelihood to accept cognitive offers compared to physical ones ($\beta$ = `r round(mixSummary$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary$Pvals["Physical", "Cognitive"])`). This initial result suggests that differences in cost decrease if individuals are able to evaluate all of them.

>>>>

## plot
earnFitplot_btw <- ggplot(data = temp, aes(pComplete, Earnings)) +
         scale_color_manual(values = colsBtw) +
         geom_point(aes(fill = Cost), pch = 21, color = "black", size = 3, show.legend = F) +
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsBtw) +
         theme(panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(),
           panel.background = element_blank(),
           axis.line = element_line(colour = "black"),
           text = element_text(size = 12))

@@

```{r General prop & earnings plots (Fig. 3), fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least."}
# plots generated in 16.2.1. and 16.1.3.
 prop1 | earnings1 | earnFitplot_btw
```

@@

# plot coefficients and pvalues in a matrix
# invert colors
col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))
# 
# corrplot(mixSummary_btw$Betas, 
#          is.corr = F, 
#          p.mat = mixSummary_btw$Pvals, 
#          type = "lower",
#          outline = T,
#          #insig = "p-value",
#          sig.level = 0.05, 
#          na.label = "square", 
#          na.label.col = "grey",
#          method = "color", 
#          tl.col = "black",
#          tl.cex = 0.8,
#          col = col2(200))

@@

  In order to test these qualitative observations, we computed the probability of accepting a trial with a mixed-effects logistic regression (see Methods for details). As predicted, and confirming previous results, the model showed significant main effects of handling time (global intercept = `r round(fixef(mixLogis_main$Wait)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Wait)["Handling"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Handling", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Handling", "Pr(>|z|)"])`) and offer amount ($\beta$ = `r round(fixef(mixLogis_main$Wait)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Wait)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Wait)[[10]]["Offer", "Pr(>|z|)"])`). In order to show the comparisons among all conditions, Figure 4B portrays the coefficients (color scale), and significance that resulted from switching the reference cost condition ("X" marks non-significant comparisons). The matrix of coefficients conveys that the cognitive effort group was significantly more likely to accept any offer than the physical ($\beta$ = `r round(mixSummary_btw$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Physical", "Cognitive"])`) and wait groups ($\beta$ = `r round(mixSummary_btw$Betas["Wait", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_btw$Pvals["Wait", "Cognitive"])`), but not the easy group.

@@

``` {r BTW: 16.3.2. Plot Pre/Post, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# scatter plot of pre/post acceptances
# first calculate the mean acceptances per cost/half to draw horizontal and vertical lines on the plot
df_mean <- dataBtw %>%
            group_by(SubjID, Cost, Block, Half) %>%
            summarise(propAccept = mean(Choice)) %>%
            group_by(SubjID, Cost, Half) %>%
            summarise(propAccept = mean(propAccept)) %>%
            spread(Half, propAccept) %>%
            group_by(Cost) %>%
            summarise(propAccept_1 = mean(Half_1),
                      propAccept_2 = mean(Half_2))

@@

# acceptances per cost across blocks
# note that because the same handling/travel time combos repeat in the same order pre/post, 1/4-2/4-3/6 are direct comparisons
prepost_btw$propBlocks <- dataBtw %>%
                         filter(Choice < 2) %>%
                         group_by(SubjID, Cost, Block) %>%
                         summarise(propAccept_subj = mean(Choice)) %>%
                         group_by(Cost, Block) %>%
                         summarize(propAccept = mean(propAccept_subj),
                                   seAccept = sd(propAccept_subj)/sqrt(nSubjs_btw)) %>%
                         ggplot(aes(Block, propAccept, color = Cost)) +
                           geom_vline(xintercept = 3.5, linetype = "dashed") +
                           geom_point(size = 2) +
                           geom_errorbar(aes(ymin = propAccept - seAccept, ymax = propAccept + seAccept, color = Cost), width = 0.1) +
                           geom_line() +
                           ylim(0, 1) +
                           labs(y = "Proportion Acccepted") +
                           scale_x_continuous(breaks = seq(6)) +
                           scale_color_manual(values = colsBtw) +
                           scale_fill_manual(values = colsBtw) +
                           theme(legend.key = element_blank(),
                                 legend.position = c(0.8, 0.3),
                                 panel.grid.major = element_blank(),
                                 panel.grid.minor = element_blank(),
                                 panel.background = element_blank(),
                                 axis.line = element_line(colour = "black"),
                                 text = element_text(size = 14))

@@

``` {r BTW: 16.3.2. Plot Pre/Post reward x handling, echo=FALSE, fig.align = "center", fig.width = 8, fig.height = 4}
# this plot divides the proportion of acceptances for each reward/handling combination per half of the experiment
hrprepostPlot_btw <-dataBtw %>%
  group_by(SubjID) %>%
  mutate(Half = ifelse(Half == "Half_1", "First Half", "Second Half")) %>%
  group_by(SubjID, Half, Handling, Cost, Offer) %>%
  summarise(pAccept = mean(Choice)) %>%
  group_by(Half, Cost, Handling, Offer) %>%
  summarise(propAccept = mean(pAccept),
            SE = sd(pAccept) / sqrt(nSubjs_btw)) %>%
  ungroup() %>%
  mutate(Offer = ifelse(Offer == 20, 12, Offer)) %>%
  ggplot(aes(Offer, propAccept, color = Cost)) +
    geom_point(size = 3, show.legend = T) +
    geom_line(size = 1, show.legend = F) +
    scale_color_manual(values = colsBtw) +
    scale_fill_manual(values = colsBtw) +
    geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.3, size = 1, show.legend = T) +
    scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1)) +
    scale_x_continuous(breaks = c(4, 8, 12), labels = c(4, 8, 20)) +
    labs(y = "Proportion Accepted") +
    facet_wrap(vars(Handling, Half), ncol = 2) +
    theme(legend.position = "bottom",
          strip.text.x = element_blank(),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(), 
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"),
          text = element_text(size = 16))

@@

``` {r WTH: 16.1.3. prop accept x earnings, echo = FALSE, include = T, fig.align="center",fig.width = 4, fig.height = 4}
# Notes: I also performed this comparing halves and block types x half, and it doesn't look like participants were accepting less to make more.
# calculate the proportions and earnings per subject, while keeping group info
temp <- dataWth %>%
  filter(rawChoice < 2) %>%
  group_by(SubjID) %>%
  summarise(Earnings = sum(Offer[Choice == 1] / 100),
            pComplete = mean(Choice)) %>%
  mutate(pComplete2 = pComplete^2) %>%
  ungroup()

@@

# plot
earnFitplot_wth <- ggplot(data = temp, aes(pComplete, Earnings)) + 
         scale_color_manual(values = colsWth) + 
         geom_point(pch = 21, color = "black", size = 3, show.legend = T) + 
         stat_smooth(aes(y = Earnings), method = "lm", formula = y ~ x + I(x^2), color = "grey30") +
         labs(x = "Proportion Completed", y = "Total Earnings (dollars)") +
         scale_fill_manual(values = colsWth) +
         ylim(12, 16) +
         theme(panel.grid.major = element_blank(), 
           panel.grid.minor = element_blank(), 
           panel.background = element_blank(), 
           axis.line = element_line(colour = "black"),
           text = element_text(size = 16))

@@

  Analyses from the previous experiment were repurposed to examine cost differences within individuals. We begun by testing the prediction that rewards would positively influence choices. A Wilcoxon signed rank test showed that individual logistic coefficients for reward amount were significantly greater than 0 (mean $\beta$ = `r round(mean(baseCoeffs$Offer), digits = 2)`, SD = `r round(sd(baseCoeffs$Offer), digits = 2)`; V = `r wilcox.test(baseCoeffs$Offer)$statistic`, *p* `r report_p(wilcox.test(baseCoeffs$Offer)$p.value)`), once again confirming that participants were properly influenced by reward amounts. Adding a coefficient that tracked prior consecutive quits indicated that only `r sum(baseCoeffs$AR_effect)` individuals were influenced by recent quit history (95% CI above or below 0), thus discarding systematic sequential effects. In terms of earnings, a linear model predicting earnings once again showed that participants who completed too few or too many trials earned the least, in line with the experimental design (Figure 8A; general linear model with quadratic term, F = `r round(summary(lmEarn)$fstatistic[1], digits = 2)`, Beta = `r round(summary(lmEarn)$coefficients[3,1], digits= 2)`, SE = `r round(summary(lmEarn)$coefficients[3, 2], digits = 2)`, R-squared = `r round(summary(lmEarn)$r.squared, digits = 2)`, *p* `r report_p(summary(lmEarn)$coefficients[3, 4])`). When assessing the optimality of acceptances for 4 and 8 cents (99% of 20 cent offers were accepted), chi-squared tests against the optimal rate of 50% showed that participants under-accepted physical effort trials (proportion accepted = `r round(summary_costvsreward["Physical", "probability"], digits = 2)`, $\chi^2$ = `r round(summary_costvsreward["Physical", "chisquared"], digits = 2)`, *p* `r report_p(summary_costvsreward["Physical", "pval"])`; all other *p* > 0.05). Despite this deviation, participants earned a similar monetary amount per cost on average (mean Cognitive = `r filter(earnings_within, Cost == "Cognitive")$mEarn`, SD = `r filter(earnings_within, Cost == "Cognitive")$sdEarn`; mean Wait_C = `r filter(earnings_within, Cost == "Wait_C")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_C")$sdEarn`; mean Physical = `r filter(earnings_within, Cost == "Physical")$mEarn`, SD = `r filter(earnings_within, Cost == "Physical")$sdEarn`; mean Wait_P = `r filter(earnings_within, Cost == "Wait_P")$mEarn`, SD = `r filter(earnings_within, Cost == "Wait_P")$sdEarn`). These results convey that participants in both experiments were similarly influenced by the characteristics of the environment, although participants in the present experiment gravitated more towards optimality (**caveat: the same percentage can be produced by many non-optimal combinations, including accepting half of each reward. So neither approach really gets at this too well.**).

@@

# plot proportion accepted per trial/offer combo
hrPlot_wth <- dataWth %>%
        filter(Choice < 2) %>%
        group_by(Cost, Offer) %>%
        summarise(propAccept = mean(Choice),
                  SE = sd(Choice) / sqrt(nSubjs_wth)) %>%
        ungroup() %>%
        mutate(Optimal = rep(c(0, 1, 1), length(unique(dataWth$Cost))),
               #BlockType = as.factor(rep(c(0,1,0,1), each = 3)),
               Offer = ifelse(Offer == 20, 12, Offer)) %>%
        ggplot(aes(Offer, propAccept, color = Cost)) +
          geom_point(size = 3, show.legend = T) +
          geom_point(aes(y = Optimal), size = 3, pch = 21, fill = "grey75", color = "grey30") +
          geom_line(lwd = 1, show.legend = T) +
          scale_color_manual(values = colsWth) +
          scale_fill_manual(values = colsWth) +
          geom_errorbar(aes(ymin = propAccept - SE, ymax = propAccept + SE), width = 0.4, size = 1) +
          scale_y_continuous(limits = c(0, 1), breaks = c(0,0.5,1)) +
          scale_x_continuous(breaks = c(4, 8, 12), labels = c("4", "8", "20")) +
          labs(y = "Proportion Accepted") +
          theme(legend.position = c(0.8, 0.25),
                legend.key = element_blank(),
                panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line = element_line(colour = "black"),
                text = element_text(size = 22))

@@

``` {r WTH: 16.2.1. mixed effects matrix, echo = FALSE, fig.align = "center", fig.width = 5,  fig.height = 4}
# get summary of coeffs
rearrange <- c("Cognitive", "Wait_C", "Wait_P", "Physical")
mixSummary_wth <- betaMatrix(mixLogis_main, rearrange = rearrange)
diag(mixSummary_wth$Pvals) <- NA

# remove uninteresting comparisons
mixSummary_wth$Betas[rbind(c(3, 1), c(4,2))] <- NA
mixSummary_wth$Pvals[rbind(c(3, 1), c(4,2))] <- NA

# corrplot makes it difficult to use this in complex layouts, so the code has been commented out to save resources

# # invert colors
# col2 <- colorRampPalette(c("#053061", "#2166AC", "#4393C3", "#92C5DE", "#D1E5F0", "#FFFFFF", "#FDDBC7", "#F4A582", "#D6604D", "#B2182B", "#67001F"))

# corrplot(mixSummary$Betas, 
#          is.corr = F, 
#          p.mat = mixSummary$Pvals, 
#          type = "lower",
#          outline = T,
#          #insig = "p-value",
#          sig.level = 0.05, 
#          na.label = "square", 
#          na.label.col = "grey",
#          method = "color", 
#          tl.col = "black",
#          tl.cex = 0.8,
#          col = col2(200))

@@

``` {r WTH: 16.2.2. ME model comparison, echo = FALSE, fig.align="center", fig.width = 6, fig.height = 4}
# fit ME logistic at increasing model complexities
mixLogis_compare <- list()
mixLogis_compare$Base <- glmer(cbind(totalAccepted, totalQuits) ~ 1 + (1 | SubjID), family = "binomial", data = mixData) # intercept only
mixLogis_compare$Cost <- glmer(cbind(totalAccepted, totalQuits) ~ Cost + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$Reward <- glmer(cbind(totalAccepted, totalQuits) ~ Offer + (1 | SubjID), family = "binomial", data = mixData)
mixLogis_compare$AllMain <- mixLogis_main$Cognitive
mixLogis_compare$Interaction <- glmer(cbind(totalAccepted, totalQuits) ~ Cost * Offer + (1 | SubjID), family = "binomial", data = mixData)

@@

# plot 
mixLogis_compare$plot <- abicLogis_compare %>% 
  gather(Comparison, Value, AIC:BIC) %>%
  mutate(Model = factor(Model, levels = names(mixLogis_compare))) %>%
  ggplot(aes(Model, Value, fill = Comparison)) +
    geom_point(color = "black", pch = 21, size = 3) +
    theme(legend.position = c(0.8, 0.8),
      legend.key = element_blank(),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      panel.background = element_blank(),
      axis.line = element_line(colour = "black"),
      text = element_text(size = 16))

@@

  Next, we addressed the hypothesis that passive waiting trials would be less costly than effortful ones. As can be seen on Figure 8B, even though the reward acceptance pattern at 10 s handling was similar to the between-subjects experiment (Figure 4A), differences among cost conditions were less evident. Moreover, these differences contradicted our predictions, as cognitive effort remained as the least costly type of demand. We tested this observation through a mixed effects logistic regression, with main fixed effects for offer amount and cost, and random subject-wise intercepts (the reference cost category was rotated in order to perform all possible pairwise comparisons). The model confirmed that increases in offer amount made acceptances significantly more likely (global intercept = `r round(fixef(mixLogis_main$Cognitive)["(Intercept)"], digits = 2)`, $\beta$ = `r round(fixef(mixLogis_main$Cognitive)["Offer"], digits = 2)`, SE = `r round(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Std. Error"], digits = 2)`, *p* `r report_p(summary(mixLogis_main$Cognitive)[[10]]["Offer", "Pr(>|z|)"])`). As in the previous section, pairwise comparison results are shown on the matrix in Figure 8C. This plot omits comparisons between effort and wait trials from different blocks, as these are not considered in our original predictions. The only significant difference was the higher likelihood to accept cognitive offers compared to physical ones ($\beta$ = `r round(mixSummary_wth$Betas["Physical", "Cognitive"], digits = 2)`, *p* `r report_p(mixSummary_wth$Pvals["Physical", "Cognitive"])`). This initial result suggests that differences in cost decrease if individuals are able to evaluate all of them.

```{r Earnings, prop completed, ME plots (Fig. 8), fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "A: Quadratic relationship between trial completions and total earnings. B: proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount). Crosses mark non-significant comparisons. D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}

include_graphics("./Images/FIG8.png")
```

  We then repeated the model comparison approach from the between-subject section, evaluating models ranging in complexity from intercept-only to a two-way interaction between cost and reward. Even though the a priori model with all main effects explained a large portion of the variance ($R^2$ = `r round(mixLogis_compare$Rsq, digits = 2)`), there were similar AIC and BIC values for any model including reward amount (Figure 8D). An analysis of deviance among the three models showed that adding cost condition to reward amount significantly improved fit (AIC~reward~ = `r filter(abicLogis_compare, Model == "Reward")$AIC`, AIC~a-priori~ = `r filter(abicLogis_compare, Model == "AllMain")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][2]`) = `r round(mixLogis_compare$aod$Chisq[2], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][2])`). However, probing the interaction between these features significantly improved fits from the main effects model (AIC~Interaction~ = `r filter(abicLogis_compare, Model == "Interaction")$AIC`, $\chi^2$(`r mixLogis_compare$aod[[7]][3]`) = `r round(mixLogis_compare$aod$Chisq[3], digits = 2)`, *p* `r report_p(mixLogis_compare$aod[[8]][3])`). (**discuss with Joe: the interaction flips results over, such that both waits > pysical effort = cognitive effort...as predicted originally? Can't wrap my head around that yet, so this conclusion is pending**)
